Looking for CDI Bias: WS Production

### 2022-01-16 03-preliminary-WSprod.Rmd
writing

>>>>

## Baseline 1PL model

```{r}
m0 <- mirt(d_mat %>% filter(rowSums(d_mat)!=0) %>% select(-data_id), 1, "Rasch", 
           technical=list(NCYCLES=1000))

coefs_1pl <- as_tibble(coef(m0, simplify = TRUE)$items) %>%
  mutate(definition = rownames(coef(m0, simplify = TRUE)$items))
fscores_1pl <- tibble(data_id = d_mat %>% filter(rowSums(d_mat)!=0) %>% select(data_id), 
                             ability = fscores(m0, method = "MAP")[,1])

save(file = here("data/eng_Ws_prod_mod_1pl.Rds"), "m0", "coefs_1pl", "fscores_1pl")
```
